FictionEro2 - Affective Impact of Fiction

### 2025-05-21 study2/analysis/2_emotion.qmd
2_emotions update

>>>>

```{r}
m1 <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition + (Condition | Participant) + (1|Stimulus),data = df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))
m2 <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition + (Condition | Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))
m3 <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition  + (Condition | Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True", Feedback_AILessAttractive=="True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))
m4 <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition  + (Condition | Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True", Feedback_AIMoreAttractive=="True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

stars2 <- data.frame(label=c("**", "***", "*", "*", "**"), 
                    Gender=fct_relevel(c("Male", "Male", "Male", "Female"), 
                                    "Male", "Female"), 
                    Type=c("All trials", "Believed trials", "'AI was less attractive'", "'AI was more attractive",
                           "Believed trials", "'AI was less arousing'"), 
                    y=c(0.65, 0.65, 0.65, 0, 0.65))

pred2 <- rbind(
  estimate_relation(m1) |> 
    mutate(Type = "All trials"),
  estimate_relation(m2) |> 
    mutate(Type = "Believed trials"),
  estimate_relation(m3) |> 
    mutate(Type = "'AI was less attractive'"),
  estimate_relation(m4) |> 
    mutate(Type = "'AI was more attractive'"))

p2 <- pred2 |> 
  mutate(Type = fct_relevel(Type, "All trials", "Believed trials", "'AI was less attractive'", "'AI was more attractive'")) |> 
  ggplot(aes(x=Type, y=Predicted)) +
  geom_hline(yintercept=0, color="darkgrey") +
  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.1) +
  geom_bar(stat="identity", aes(fill=Condition), position = position_dodge(width=0.2), width=0.2, alpha=0.6) +
  geom_pointrange(aes(ymin = CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2), size=0.2) +
  geom_rect(data=data.frame(Type="All trials", Predicted=0.1, Gender=as.factor("Male")),
            aes(xmin=0.7, xmax=1.3, ymin=0.35, ymax=0.55), color="#8BC34A", alpha=0) +
  geom_rect(data=data.frame(Type="All trials", Predicted=0.1, Gender=as.factor("Female")),
            aes(xmin=0.7, xmax=1.3, ymin=0.30, ymax=0.48), color="#8BC34A", alpha=0) +
  # geom_text(data=stars2, aes(y=y, label=label), hjust=0.5, size=3) +
  facet_grid(~Gender) +
  scale_y_continuous(labels=scales::percent) +
  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  labs(y="Arousal",
       tag = "B") +
  theme_minimal() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle=25, hjust=1, vjust=1.1, size=9),
        axis.text.y = element_text(size = 8),
        axis.title.y = element_text(size = 10),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 10),
        legend.position = "none")

p2
